\chapter{Design of excitation signals}
\def\thisDir{ch02-qlogms}
\researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}

\section{Introduction}
\label{sec:excitation:intro}
Experiment design is the first step in the system identification loop, as illustrated in \figref{fig:intro:identification-cycle}.
Consequently, the design that is chosen influences every further step in the identification process and limit the model quality that can be attained.
In many cases

\subsection{Generic excitation signals}
\label{sec:excitation:intro:generic}


\subsection{Optimal excitation signals}
\label{sec:excitation:intro:optimal}
Since generic excitation signals are not specifically geared towards the particular system under test, such signals tend to waste signal power.

, such signals essentially don't use all the available signal power to reduce the uncertainty in the estimate.


\subsection{Robust excitation signals}
\label{sec:excitation:intro:robust}
As illustrated above, optimal experiment design places the user in a catch-22 situation.

\subsection{Approach in this chapter}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of generic and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used but its properties are tuned in such a way that it 

\input{ch02-qlogms/logMS_IMTC.tex}

\input{ch02-qlogms/sysid.tex}

\section{\TODO{Robust vs optimal}}
\section{\TODO{Robust QLog MS}}
\subsection{\TODO{Constraints: time and power}}
\subsection{\TODO{Informativity of experiment}}
\subsection{\TODO{Normalized design w.r.t. damping}}
\subsection{\TODO{Grid misalignment effects}}
\subsection{\TODO{qLog design rules}}



\section{Conclusion}
\label{sec:excitation:conclusion}
In this chapter we have illustrated that quasi-logarithmic multisine excitations are a well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.

The suggested amplitude compensation methods allow the user to measure a parametric LTI model for systems in a wide frequency band with a constant uncertainty.
The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
In practical applications, this slight increase is likely to be negligible.
The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.

We have also shown an effective way to choose the frequency spacing of a (quasi)-logarithmically spaced multisine for an equidamped set of systems.
The presented method allows to select a maximal value for the frequency ratio $\alpha = 1 + \damping$ for which the performance will not suffer from the unavoidable misalignment of the system with respect to the excited frequencies.
In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.

\TODO{omrekentabel verschillende grootheden: $F$, $F/\mathrm{dec}$, $F/\mathrm{oct}$, $\alpha$, $\delta f$}


\begin{subappendices}
  \section{Justification for considering only poles}

\end{subappendices}


